First Measurements of the D(e,e'p)n Cross Section at \\ Very High Recoil Momenta and Large Q^{2}

### 2020-01-06 MY_PUBLICATIONS/PRL/draft_v3/body.tex
updated

\indent Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum $p_{r}$ for three angular settings at $Q^{2}=4.5\pm0.5$
(GeV/c)$^{2}$. The results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (cyan). The data is compared to theoretical reduced
cross sections using the charge-dependent Bonn (CD-Bonn)\cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38} and Paris\cite{PhysRevC.21.861} NN-potentials. The theoretical calculations
for the CD-Bonn (magenta) and AV18 (green) potentials were performed by M. Sargsian\cite{PhysRevC.82.014612} and those for the Paris (blue) potential were done by J.M. Laget\cite{LAGET2005}. \\
\indent For the recoil angles shown in Fig. \hyperref[fig:fig1]{1(a)-(c)}, all models agree and the cross sections are dominated by the PWIA up to $p_{r}\sim$300 MeV/c, which corresponds to the long-range part
of the NN-potential which is well understood. Beyond $p_{r}\sim$300 MeV/c, at recoil angles $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and AV18 model cross sections are dominated by
the PWIA and are within good agreement whereas the CD-Bonn calculation exhibits a different behaviour which indicates a larger sensitivity to the different NN-potentials
at higher missing momenta. At recoil angles $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig1]{1(c)}] and $p_{r}>300$MeV/c, FSIs become dominant and exhibit a similar behaviour among all models which obscures any possibility
of extracting the momentum distributions at these angles. \\

@@

\indent The ratio of the experimental and theoretical reduced cross sections ($\sigma_{red}$) to the deuteron momentum distributions (n$(p_{r})$) is shown in Fig. \ref{fig:fig2}. As a reference we selected the
deuteron momentum distribution calculated using the charge-dependent Bonn (CD-Bonn) potential\cite{PhysRevC.63.024001}.
\begin{figure}[h!]
\includegraphics[scale=0.5]{../prl_plots/PRL_plot2.pdf}
\caption{The ratio R($p_{r}$) = $\sigma_{red}$/n$(p_{r})$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$. The dashed reference (magenta) line refers to CD-Bonn momentum distribution (n$(p_{r})$) by which the data and all models are divided. }
\label{fig:fig2}
\end{figure} \\
\indent At $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig2]{2(c)}], there is a clear onset of GEA at $p_{r}\gtrsim300$ MeV/c where FSI become dominant as indicated by the rise of FSI (solid lines) for
all theoretical calculations as compared to the reference. In this region, our experiment is statistically limited as we focused on kinematics at lower recoil angles where FSIs are small. The overlayed
Hall A data, however, shows excellent agreement with the Paris FSI. For $p_{r}<300$ MeV/c, FSIs are small as indicated by the approximate ratio R$\sim$1 for all the theoretical calculations using FSI, which the
data follows. The small dip observed in this region (R$<1$) is indicative of the approximate (not exact) cancellation between the PWIA/FSI interference (screening term) and the modulus-squared of FSI (re-scattering) terms in
the cross section. \\
\indent For $\theta_{nq}=45^{o}$ [Fig. \hyperref[fig:fig2]{2(b)}] at $p_{r}<300$ MeV/c, all theoretical calculations agree with each other and are sensitive to the momentum distribution inside the deuteron which
the data confirms. At $p_{r}\gtrsim300$ MeV/c, the Paris/AV18 calculations start to deviate from the CD-Bonn calculations, with the most substantial deviations observed at $p_{r}\sim 1$ GeV/c.
The CD-Bonn calculations are sensitive to momentum distributions up to $p_{r}\sim$580 MeV/c before FSIs start to dominate (R$>1$).
The data agrees well with the CD-Bonn PWIA calculation but show an earlier rise than predicted by the CD-Bonn FSI, a behaviour which is not described by any of the models. \\
\indent A similar behaviour is observed for $\theta_{nq}=35^{o}$ [Fig. \hyperref[fig:fig2]{2(a)}], where the CD-Bonn calculations are sensitive to momentum distributions up to $p_{r}\sim800$ MeV/c before being
overwhelmed by FSIs, whereas the Paris/AV18 calculations start to deviate from the CD-Bonn at $p_{r}\sim300$ MeV/c. The data shows sensitivity to CD-Bonn momentum distributions up to $p_{r}\sim$750 MeV/c before
exhibiting an earlier rise than predicted by CD-Bonn FSI. \\ 
\indent The $\theta_{nq}=35^{o}$ [Fig. \hyperref[fig:fig2]{2(a)}] appears to be the optimal kinematics to study the high momentum components of the deuteron wavefunction, as the data is sensitive to momentum
distributions up to $p_{r}\sim750$ MeV/c as compared to $p_{r}\sim$580 MeV/c for the $\theta_{nq}=45^{o}$ setting. \\
%-------------------------------------------------------------------------------------------------------------------------------
%----------CONCLUSION----------
\indent This experiment extended the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 
unprecedented large $Q^{2}$ and very high neutron recoil momenta at kinematics that enhanced the high momentum components of the deuteron wavefunction.
The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data. Furthermore, the CD-Bonn calculations
were found to be sensitive to momentum distributions up to $p_{r}\sim800$ MeV/c for recoil angles $\theta_{nq}=35\pm5^{o}$, which the data agreed
up to $p_{r}\sim750$ MeV/c. At higher missing momentum, however, all models are unable to describe the data, which is currently not well understood.\\
\indent Given that this was a commissioning experiment that ran for only 6 out of the 42 days (14.2$\%$) of beam time and 3 out of the 8 original kinematic settings,
additional beam time would be required to measure the full kinematic coverage (more missing momentum settings) to gain the necessary statistics 
in order to make any definitive arguments about the underlying physics observed. \\
\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
to the equipment for the Hall C upgrade making all four commissioning experiments possible.

>>>>

%:::::Rather than saying sensitivity to different NN potentials, say explicitly: "Up to 300 MeV/c, all models use a similar long-range part of the NN potential. Above 300 MeV/c, corresponding to the medium and short
% range parts of the NN potential, The Paris/AV18 PWIA agree, whereas the CD-Bonn PWIA is different, which indicates the NN potentials in the medium to short range parts greatly differe between the CD-Bonn and Paris/AV18.
%no model describes the data over the entire range--the data has a different shape than any of the models."

\indent Figure \ref{fig:fig1} shows the extracted experimental and theoretical reduced cross sections as a function of neutron recoil momentum $p_{r}$ for three angular settings at $Q^{2}=4.5\pm0.5$
(GeV/c)$^{2}$. The results from the previous Hall A experiment\cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (cyan). The data is compared to theoretical reduced
cross sections using the charge-dependent Bonn (CD-Bonn)\cite{PhysRevC.63.024001}, Argonne $v_{18}$ (AV18)\cite{PhysRevC.51.38} and Paris\cite{PhysRevC.21.861} NN-potentials. The theoretical calculations
for the CD-Bonn (magenta) and AV18 (green) potentials were performed by M. Sargsian\cite{PhysRevC.82.014612} and those for the Paris (blue) potential were done by J.M. Laget\cite{LAGET2005}. \\
\indent For the recoil angles shown in Fig. \hyperref[fig:fig1]{1(a)-(c)}, all models agree and the cross sections are dominated by the PWIA up to $p_{r}\sim$300 MeV/c, which corresponds to the long-range part
of the NN-potential which is well understood. Beyond $p_{r}\sim$300 MeV/c, at recoil angles $\theta_{nq}=35^{o}$ and $45^{o}$ [Figs. \hyperref[fig:fig1]{1(a), 1(b)}], the Paris and AV18 model cross sections are dominated by
the PWIA and are within good agreement up $p_{r}\sim750$ MeV/c, whereas the CD-Bonn calculation exhibits a different behaviour which indicates a larger sensitivity on the momentum distribution to the different NN-potentials
at higher missing momenta. At recoil angle $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig1]{1(c)}], FSIs become dominant at $p_{r}>300$MeV/c and exhibit a similar behaviour among all models which obscures any possibility
of extracting the momentum distributions at these angles. \\

% Make a transition between plot 1 and plot 2 to indicate the reason why we take the ratio: Since the shape of the data does not fully agree with any of the models >300 MeV/c, a ratio is taken to
% make sense out of the discrepancy obsevred, and try to understand why are the shapes different. More information can be obtained from a ratio plot, by comparing different calculations relative to the CD-Bonn.

@@

%In plot 2: mention that the data disagrees with the AV18/Paris by about R = 2.5.  Also note that since we understand how FSIs work from th_nq= 75 deg,  FSIs should be well understood at the 35 and 45 deg settings.

\indent The ratio of the experimental and theoretical reduced cross sections ($\sigma_{red}$) to the deuteron momentum distributions ($\sigma^{\textrm{\small CD-Bonn PWIA}}_{red}$) is shown in Fig. \ref{fig:fig2}.
As a reference we selected the deuteron momentum distribution calculated using the charge-dependent Bonn (CD-Bonn) potential\cite{PhysRevC.63.024001}.
\begin{figure}[h!]
\includegraphics[scale=0.5]{../prl_plots/PRL_plot2.pdf}
\caption{The ratio R($p_{r}$) = $\sigma_{red}/\sigma^{\textrm{\small CD-Bonn PWIA}}_{red}$ is shown in (a)-(c) for $\theta_{nq}=35^{o}, 45^{o}$ and $75^{o}$, respectively, each with a bin width of $\pm 5^{o}$.
The dashed reference (magenta) line refers to CD-Bonn PWIA calculation (or momentum distribution) by which the data and all models are divided.}
\label{fig:fig2}
\end{figure} \\
\indent For $\theta_{nq}=35^{o}$ and $45^{o}$ [Fig. \hyperref[fig:fig2]{2(a)-(b)}] the data is best described by the CD-Bonn PWIA calculation for recoil momenta up to $p_{r}\sim700$ MeV/c and $\sim580$ MeV/c, respectively.
The data shows a larger sensitivity to the CD-Bonn deuteron momentum distributions at smaller neutron recoil angles ($\theta_{nq}=35^{o}$) which indicates this is the optimal kinematic setting to probe the deuteron
wavefunction larger missing momenta. Furthermore, the agreement between the Halls A and C data solidifies the approach of selecting a kinematic region where recoil angles are small and FSIs are reduced.
At larger recoil momenta where the ratio is $R>1$ and FSIs dominate the cross section models, the data is not well described by any of the models and exhibits a rise in the ratio which is not well understood.
This hign missing momentum region is statistically limited and additional data would be required before any conclusions can be made. \\
\indent At $\theta_{nq}=75^{o}$ [Fig. \hyperref[fig:fig2]{2(c)}], there is a clear onset of GEA at $p_{r}\gtrsim300$ MeV/c where FSI become dominant as indicated by the rise of FSI (solid lines) for

%-------------------------------------------------------------------------------------------------------------------------------
%----------CONCLUSION----------
\indent This experiment extended the previous Hall A cross section measurements on the $^{2}H(e,e'p)n$ reaction to 
unprecedented large $Q^{2}$ and very high neutron recoil momenta at kinematics that enhanced the high momentum components of the deuteron wavefunction.
The experimental reduced cross sections were extracted and found to be in good agreement with the Hall A data. Furthermore, the CD-Bonn calculations
were found to be sensitive to momentum distributions up to $p_{r}\sim800$ MeV/c for recoil angles $\theta_{nq}=35\pm5^{o}$, which the data agreed
up to $p_{r}\sim750$ MeV/c. At higher missing momentum, however, all models are unable to describe the data, which is currently not well understood.\\
\indent Given that this was a commissioning experiment that ran for only 6 out of the 42 days (14.2$\%$) of beam time and 3 out of the 8 original kinematic settings,
additional beam time would be required to measure the full kinematic coverage (more missing momentum settings) to gain the necessary statistics 
in order to make any definitive arguments about the underlying physics observed. \\
\indent We acknowledge the outstanding support of the staff of the Accelerator and Physics Divisions at Jefferson Lab
as well as the entire Hall C staff, technicians, graduate students and users who took shifts or contributed
to the equipment for the Hall C upgrade making all four commissioning experiments possible.
